---
title: "ProcessDeliveryAnalysis"
date: "April 30, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data, baltimore city stats, and do a join

```{r cars}
library(dplyr)
library(ggmap)

#default.data <- read.csv("defaultCasesOverServerAndZipcode.csv", sep="\t")
default.data <- read.csv("defaultCasesOverServerAndZipcodeModifiedCaseCriteria.csv", sep="\t")
default.data$DefendantZip <- as.factor(default.data$DefendantZip)
service.data <- read.csv("serviceStatsOverServerAndZipcode.csv", sep="\t")

bmore.stats <- data.frame(
  zipcodes=factor(c(21207,21209, 21210, 21211,21212, 21213,21215,21214,21217,21216,21218,21223,21224, 21225,21226,21229,21231,21230 ,21239, 21251,21263,21287,21201,21202,21205)),
  med.income=c(52253, 73577, 83051, 57572, 65450, 32317, 34885, 63412, 27382, 33857, 37959, 26342, 56997, 37992,  65625, 44485, 57071, 67132, 50809, NA, NA, NA, 30853, 31638, 24187))

# for presentation, just show the relevant ones to paint our picture
bmore.stats <- bmore.stats[c(6,7,9,11),]

geo.coords <- read.csv("zipCodeGeoCoordLongLat.csv")
geo.coords$ZIP <- as.factor(geo.coords$ZIP)
bmore.stats <- inner_join(bmore.stats, geo.coords, by=c("zipcodes" = "ZIP"))

default.data <- inner_join(default.data, bmore.stats['zipcodes'], by=c("DefendantZip" = "zipcodes"))
default.data$DefendantZip <- as.factor(default.data$DefendantZip)
service.data <- inner_join(service.data, bmore.stats['zipcodes'], by=c("DefendantZip" = "zipcodes"))
service.data$DefendantZip <- as.factor(service.data$DefendantZip)
```

Plot an income map image
```{r}
qmap("Baltimore, MD", zoom=12) + geom_point(data=bmore.stats, aes(x=LNG, y=LAT, color=med.income, size=med.income))

```

## Visualizing defaulting stats


Plot the raw number of defaults on a map
```{r}
default.result <- default.data %>% group_by(DefendantZip) %>% summarize(numberDefaultedCases = sum(numDefaults)) %>% inner_join(bmore.stats, by=c("DefendantZip" = "zipcodes")) %>% arrange(desc(numberDefaultedCases)) %>%  as.data.frame()

qmap("Baltimore, MD", zoom=12) + geom_point(data=default.result, aes(x=LNG, y=LAT, color=numberDefaultedCases, size=numberDefaultedCases))

```



For each zip code, find the percentage of cases that are a default settlement.
```{r, echo=FALSE}

default.result <- default.data %>% group_by(DefendantZip) %>% summarize(percentDefault = sum(numDefaults)/sum(totalNumCases)) %>% inner_join(bmore.stats, by=c("DefendantZip" = "zipcodes")) %>% arrange(desc(percentDefault)) %>%  as.data.frame()

```

Plot the results
```{r}
ggplot(data=default.result) + geom_line(aes(x=1:nrow(default.result), y=percentDefault))
```
Plotting percent default by median income of the region
```{r}
ggplot(data=default.result) + geom_point(aes(x=med.income, y=percentDefault)) + labs(x="Median Income", y="Percentage of Defaulted Cases")
```

Plot the percentages on a map
```{r}
qmap("Baltimore, MD", zoom=12) + geom_point(data=default.result, aes(x=LNG, y=LAT, color=percentDefault, size=percentDefault))


```
Table of highest overall number of civil cases in general:
```{r}
library(gtable)
library(grid)
library(gridExtra)
default.res3 <- default.data %>% group_by(DefendantZip) %>% summarize(totalNumberCases = sum(totalNumCases)) %>% arrange(desc(totalNumberCases))


table <- tableGrob(default.res3, rows=NULL)
title <- textGrob("Test", gp = gpar(fontsize = 10))
padding <- unit(0.5,"line")
table <- gtable_add_rows(
  table, heights = grobHeight(title) + padding, pos = 0
)
table <- gtable_add_grob(
  table, list(title),
  t = 1, l = 1, r = ncol(table)
)
grid.newpage()
grid.draw(table)


```

Find the how the case resolutions are distributed across regions, and also how the default cases are distributed.
```{r}
default.res2 <- default.data %>% group_by(DefendantZip) %>% summarize(totalNumDefaults = sum(numDefaults), totalNotDefaults = sum(totalNumCases) - sum(numDefaults)) %>% tidyr::gather("DefaultsResult", "Count", 2:3)
#ggplot(data=default.res2, aes(DefendantZip)) + geom_bar(aes(weight = totalNumDefaults)) + labs(x="Zip Code", y="Number of Defaulted Cases")


ggplot(data=default.res2, aes(x = DefendantZip, y = Count, fill = DefaultsResult)) + geom_bar(stat="identity") + scale_fill_discrete(name="Default Case Breakdown",labels=c("Case Not Defaulted", "Case Defaulted"))

```


## Visualizing service stats

Show the percentage of processes that are actually served for each zip code.
```{r, echo=FALSE}

service.result <- service.data %>% group_by(DefendantZip) %>% summarize(percentServed = sum(numSV)/sum(totalNumCases)) %>%
inner_join(bmore.stats, by=c("DefendantZip" = "zipcodes")) %>% arrange(percentServed) %>%  as.data.frame()

```

```{r}
ggplot(data=service.result) + geom_line(aes(x=1:nrow(service.result), y=percentServed))
```

Plotting area percentage of processes served as function of med income
```{r}
ggplot(data=service.result) + geom_point(aes(x=med.income, y=percentServed)) + labs(x="Median Income", y="Percentage of Processes Served")
```


Find the how the case resolutions are distributed across regions, and also how the default cases are distributed.
```{r}
service.res2 <- service.data %>% group_by(DefendantZip) %>% summarize(totalNumServed = sum(numSV), totalNotServed = sum(totalNumCases) - sum(numSV)) %>% tidyr::gather("ServiceResult", "Count", 2:3)
# ggplot(data=service.res2, aes(DefendantZip)) + geom_bar(aes(weight = totalNumServed)) + labs(x="Zip Code", y="Number of processes served")
ggplot(data=service.res2, aes(x = DefendantZip, y = Count, fill = ServiceResult)) + geom_bar(stat="identity")
```

Plot the percentages on a map
```{r}
qmap("Baltimore, MD", zoom=12) + geom_point(data=service.result, aes(x=LNG, y=LAT, color=percentServed, size=percentServed))


```
